A performance comparison of Dask and Spark for data-intensive neuroimaging pipelines

### 2019-07-25 latex/paper.tex
Worked on results section for  histo, hitso (NumPy) and modified results section for Bids

In Figure~\ref{fig:inc_tt_itr}, the total execution time breakdown is
shown. We observe good scalability of all the engines with the number of
iterations.

@@

From Figure~\ref{fig:histo_tt_worker} the total time spend in each function is shown.
The computation time is significantly larger in Dask than Spark. This is potentially
due to Python's GIL preventing Dask to parallelize the computation on multiple thread.
Overall, the IO and overhead is comparable for all engines.

@@

\subsection{Histogram: Number of blocks}
Figure~\ref{fig:histo_ms_block}

@@

\subsection{Histogram (NumPy): Number of workers}
Figure~\ref{fig:histo_np_ms_worker}

From Figure~\ref{fig:histo_np_tt_worker}

@@

\subsection{Histogram (NumPy): Number of blocks}
Figure~\ref{fig:histo_np_ms_block}

@@

@@

%% Baseline gantt chart
\subsection{BidsApp example: Gantt chart}
Figure~\ref{fig:bids_gantt} shows the Gantt charts obtained for each engine and API.
The Gantt charts are structured in three main parts: participant analysis (orange),
group analysis (blue), and the transition in between.\MD{rephrase} The Gantt chart
for Spark seems to have more workers however it does not. This is due to the
computation of the participant and group analysis on two different jobs with their
worker processes; usually with different process id. The tasks differ considerably in
length. This is due to the high IO requirement of the application. During the
participant analysis phase, Spark and Futures have less overhead than Delayed and
Bag. At the end of the participant analysis phase, Futures and Delayed has less
overhead than Bag while Spark has way more than Dask engine. The group analysis is
similar for all engines and APIs.

>>>>

In Figure~\ref{fig:inc_tt_itr}, the total execution time breakdown is
shown. We observe good scalability of all the engines with the number of
iterations.
% TODO

@@

From Figure~\ref{fig:histo_tt_worker} the total time spend in each function is shown.
The computation time is significantly larger in Dask than Spark. This is potentially
due to Python's GIL preventing Dask to parallelize the computation on multiple threads.
Overall, the IO and overhead is comparable for all engines.

@@

\subsection{Histogram: Number of blocks}
Figure~\ref{fig:histo_ms_block} shows the makespan for different block size.
Again, Spark is significantly faster then Dask engines and Bag is slightly faster
than Delayed. Overall, the engines do not react to change in block size.

In figure~\ref{fig:histo_tt_block} 
%TODO

@@

\subsection{Histogram: Gantt chart}

\begin{figure}[!htb]
    \centering
    \begin{subfigure}[b]{\columnwidth}
        \includegraphics[clip,width=\columnwidth]{images/spark_histo_gantt.png}
        \caption{Spark}\label{fig:histo_spark_gantt}
    \end{subfigure}
    \\
    \begin{subfigure}[b]{\columnwidth}
        \includegraphics[clip,width=\columnwidth]{images/bag_histo_gantt.png}%
        \caption{Dask Bag}\label{fig:histo_dask_bag_gantt}
    \end{subfigure}
    \\
    \begin{subfigure}[b]{\columnwidth}
        \includegraphics[clip,width=\columnwidth]{images/delayed_histo_gantt.png}%
        \caption{Dask Delayed}\label{fig:histo_dask_delayed_gantt}
    \end{subfigure}
    \caption{Histogram: Gantt chart with 125 blocks, 10 iterations, \SI{4}{\second}
delay, 8 workers, 8 threads/worker}\label{fig:histo_gantt}
\end{figure}

%%% HISTOGRAM (NumPy) %%%
\subsection{Histogram (NumPy): Number of workers}
Figure~\ref{fig:histo_np_ms_worker} shows the makespan for various amount fo workers.
Overall, the makespan for all engines does not change considerably with an increase 
in worker. This is beacuse the engines do not scale well.

On figure~\ref{fig:histo_np_ms_worker}, there is no substantial difference between
 all engines, althought, Delayed is slightly faster.

From Figure~\ref{fig:histo_np_tt_worker}, the total execution time spent in each
function is shown. The overhead and read time increase proportionally to the number
of workers thus increasing the total time. This is because (1) most worker read at
the same time due to a low computation-IO ratio and (2) \MD{Determine why the
overhead is so large compared to the pure Python implementation}

@@

\subsection{Histogram (NumPy): Number of blocks}
Figure~\ref{fig:histo_np_ms_block} shows the makespan of the application for
different block size. Note that the workers can process up to 64 tasks in paralle thus
they are not used at full capacity with 30 blocks. Overall, there is no substantial
difference for all engines and block size.

In figure~\ref{fig:histo_np_tt_block}, shows the total time spent in each function.
Again, the overhead for 30 blocks is erroneous due a lower amount of task than thread
which result in higher overhead for thread based engines. Considering the overhead
error and that at 30 blocks the worker only use half their core, the  total time is
substantially the same for all block size. This is due lower block sizes having a
lower IO time, however, it is balanced by the resulting increase in overhead.

@@

\subsection{Histogram (NumPy): Gantt chart}

\begin{figure}[!htb]
    \centering
    \begin{subfigure}[b]{\columnwidth}
        \includegraphics[clip,width=\columnwidth]{images/spark_histo_np_gantt.png}
        \caption{Spark}\label{fig:histo_np_spark_gantt}
    \end{subfigure}
    \\
    \begin{subfigure}[b]{\columnwidth}
        \includegraphics[clip,width=\columnwidth]{images/bag_histo_np_gantt.png}%
        \caption{Dask Bag}\label{fig:histo_np_dask_bag_gantt}
    \end{subfigure}
    \\
    \begin{subfigure}[b]{\columnwidth}
        \includegraphics[clip,width=\columnwidth]{images/delayed_histo_np_gantt.png}%
        \caption{Dask Delayed}\label{fig:histo_np_dask_delayed_gantt}
    \end{subfigure}
    \caption{Histogram (NumPy): Gantt chart with 125 blocks, 10 iterations, \SI{4}{\second}
delay, 8 workers, 8 threads/worker}\label{fig:histo_np_gantt}
\end{figure}

@@

%% Baseline gantt chart
\subsection{BidsApp example: Gantt chart}
Figure~\ref{fig:bids_gantt} shows the Gantt charts obtained for each engine and API.
The Gantt charts are structured in two main parts: participant analysis (orange) and
group analysis (blue). The participant analysis tasks differ greatly in lenght. This
is due to inqual amount of sessions per subject to process. The group analysis is
similar for all engines and APIs. Overall, most of the overhead encountered results
from the transition between the two analysis. This is because the group analysis is
requires the results of the participant analysis to start.
